\documentclass[10pt,letterpaper]{article}

% Packages
\usepackage[margin=0.5in]{geometry} % Narrower margins to fit everything on 1 page
\usepackage{titlesec} % For section formatting
\usepackage{enumitem} % For list formatting
\usepackage{hyperref} % For links
\usepackage{xcolor}   % For link colors
\usepackage{fancyhdr}

% Formatting Settings
\newcommand{\resumepagetotal}{2} % set to match PDF page count (e.g. 2 or 3)
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\footnotesize\textbf{Brendan Premo} \quad\textbar\quad Page \thepage\ of \resumepagetotal}
\setlength{\footskip}{18pt}
\urlstyle{same} % Makes URLs look like normal text

% Section Formatting
\titleformat{\section}
  {\large\bfseries\uppercase} % Format: Large, Bold, Uppercase
  {}
  {0em}
  {}[\titlerule] % Adds a horizontal line after the section title

\titlespacing{\section}{0pt}{10pt}{5pt} % Spacing around sections

% List Formatting
\setlist[itemize]{leftmargin=*}

\begin{document}

%---------------------------------------------------
%   HEADER
%---------------------------------------------------
\begin{center}
    {\Huge \textbf{Brendan Premo}} \\ \vspace{4pt}
    Troy, NY \ $|$ \ (518) 588-0855 \ $|$ \ \href{mailto:bdanp1998@gmail.com}{bdanp1998@gmail.com} \\
    \href{https://www.linkedin.com/in/premobrendan/}{linkedin.com/in/premobrendan} $|$ 
    \href{https://github.com/premobrendan/portfolio}{github.com/premobrendan/portfolio}
\end{center}

%---------------------------------------------------
%   TECHNICAL SKILLS
%---------------------------------------------------
\section*{Technical Skills}
\begin{itemize}[noitemsep, topsep=0pt]
    \item \textbf{Languages:} Python, SQL, R, Java, Excel, Jupyter, \LaTeX
    \item \textbf{Libraries \& Tools:} PyTorch, Scikit-Learn, Pandas, GitHub, AutoGluon, Power BI (Sigma Computing)
    \item \textbf{Machine Learning:} Convolutional Neural Networks (CNN), Transfer Learning, Gradient Descent, Random Forest, Feature Engineering, Alternating Least Squares (ALS), Regression (Multivariate, Logistic, Time Series)
    \item \textbf{Data Analysis:} EDA, ETL, Statistics (Bayesian, Inferential and Nonparametric), KPIs, Trend Analysis, Variance Analysis, Validation
    \item \textbf{Mathematics:} Topological Data Analysis (TDA), Markov Chains, Monte Carlo Simulations, Principal Component Analysis (PCA), k-Rank SVD
    \item \textbf{Healthcare-Specific Analysis:} Claims, Readmissions, Length of Stay, Utilization, Costs, Insurance Plans (Medicaid, Medicare, Private), EMR/EHR, Medical Loss Ratio (MLR)
\end{itemize}

%---------------------------------------------------
%   PROFESSIONAL EXPERIENCE
%---------------------------------------------------
\section*{Professional Experience}

\noindent \textbf{Soria Research} \hfill \textit{Data Analyst} \\
\textit{June 2025 -- April 2026} \hfill \textit{Remote}
\begin{itemize}[noitemsep, topsep=2pt]
    \item Created the visual architecture of our products in Sigma, personally designed or refined over 75\% of all client-facing analytical materials, specifically within the Healthcare sector.
    \item Orchestrated and developed end-to-end data pipelines, managing data acquisition, cleaning, and complex analysis for future use in the product, spanning EMR, EHR, and public health data, with emphasis on MLR, enrollment, and year-over-year deltas for companies and providers in the sector.
    \item Onboarded and trained new analysts on internal systems and data best practices.
\end{itemize}

%---------------------------------------------------
%   EDUCATION
%---------------------------------------------------
\section*{Education}

\noindent \textbf{University at Albany} \hfill Albany, NY \\
\textit{Master of Science in Data Science} \hfill \textit{Fall 2023 -- Spring 2025}\\
\textit{Master of Arts in Mathematics} \hfill \textit{Fall 2022 -- Fall 2024}

\vspace{4pt}

\noindent \textbf{Rensselaer Polytechnic Institute (RPI)} \hfill Troy, NY \\
\textit{Bachelor of Science in Applied Mathematics} \hfill \textit{Fall 2016 -- Fall 2020}

%---------------------------------------------------
%   KEY PROJECTS
%---------------------------------------------------
\section*{Key Technical Projects}

\noindent \textbf{Hospital Cost Report (Soria Analytics Dashboard, Sigma)} \hfill \textit{Winter 2025 -- Spring 2026}
\begin{itemize}[noitemsep, topsep=2pt]
    \item Created an interactive dashboard for the annual CMS Hospital Provider Cost Report dataset, breaking down national and provider-specific metrics (Revenue, Costs, Margins, Occupancy and Discharges).
    \item Set up a pipeline including a web crawler to automatically detect RSS feed updates for data, a scraper for automatic download, schema detection protocols to find deviations in formatting, and a system to incorporate the newly uploaded data directly into the dashboard.
\end{itemize}

\vspace{1pt}

\noindent \textbf{Star Ratings (Soria Analytics Script, Python)} \hfill \textit{Fall 2025 -- Winter 2025}
\begin{itemize}[noitemsep, topsep=2pt]
    \item Developed a script that takes the raw Star Ratings tables from CMS and reconciles star ratings by plan.
    \item Analyzed plans individually, showing star rating changes from previous years as well as the metric shifts that caused the changes.
    \item Analyzed companies in aggregate by tracking changes in their plans' star ratings over time among NYSE-listed parent companies; Star Ratings are a well-known driver of trading interest, with share-price reactions often on the order of 5--10\% depending on enrollment-weighted average star rating.
\end{itemize}

\vspace{1pt}

\noindent \textbf{CDC Weekly Hospital Inpatient/ICU Occupancy (Soria Analytics Dashboard, Sigma)} \hfill \textit{Fall 2025}
\begin{itemize}[noitemsep, topsep=2pt]
    \item Designed an in-depth dashboard showing Influenza-like Illness statistics over time, highlighting trends from season to season and allowing for aggregation based on varying timeframes.
    \item Includes optional breakdowns of trends based on age group to show differences in this demographic over time as well as in different regions (Census and HHS).
    \item Provides various visualizations of the data to suit individual preferences.
    \item Maintains a full end-to-end data pipeline so the dashboard updates each week when new data is released.
\end{itemize}

\vspace{1pt}

\newpage

\noindent \textbf{Biomechanics Topological Data Analysis (Data Science Thesis)} \hfill \textit{Spring 2025}
\begin{itemize}[noitemsep, topsep=2pt]
    \item Analyzed movement patterns in sports video data to distinguish between optimal and suboptimal form.
    \item Transformed dynamic video into grayscale pixel data to perform Persistent Homology using Python, successfully mapping movement topology.
    \item Delivered a professional technical report and presentation summarizing complex topological findings for stakeholders.
\end{itemize}

\vspace{1pt}

\noindent \textbf{Riemann Spectrum \& Analytic Continuation (Mathematics Thesis)} \hfill \textit{Spring 2024}
\begin{itemize}[noitemsep, topsep=2pt]
    \item Conducted extensive research on the history and formulations of the Riemann Hypothesis, focusing on analytic continuation.
    \item Developed and delivered a four-part lecture series to graduate students and professors, synthesizing complex theoretical mathematics into accessible presentations.
\end{itemize}

\vspace{1pt}

\noindent \textbf{Machine Learning Projects: Predictive Modeling \& Systems} \hfill \textit{Spring 2025}
\begin{itemize}[noitemsep, topsep=2pt]
    \item \textbf{Housing Price Prediction:} Engineered a predictive model achieving a normalized Root Mean Square Error (RMSE) of 0.07 by utilizing AutoGluon’s Tabular Predictor; performed extensive data cleaning and feature engineering.
    \item \textbf{Recommendation System:} Developed a movie/music recommendation engine from scratch, implementing Alternating Least Squares (ALS), Stochastic Gradient Descent (SGD), and Projected Gradient algorithms without relying on pre-built libraries.
    \item \textbf{Image Classification (CNN):} Achieved 85\% classification accuracy on the CIFAR-10 dataset by implementing Convolutional Neural Networks; utilized transfer learning with AlexNet to demonstrate incremental network improvements.
    \item \textbf{Time Series Regression:} Conducted analysis on environmental factors, identifying a correlation where higher temperatures and lower precipitation serve as markers for higher Air Quality Index (AQI) levels.
\end{itemize}

\end{document}